---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Assignment 2



An NOAA dataset has been stored in the file `weather.csv`. This is the dataset to use for this assignment. Note: The data for this assignment comes from a subset of The National Centers for Environmental Information (NCEI) [Daily Global Historical Climatology Network](https://www1.ncdc.noaa.gov/pub/data/ghcn/daily/readme.txt) (GHCN-Daily). The GHCN-Daily is comprised of daily climate records from thousands of land surface stations across the globe.

Each row in the assignment datafile corresponds to a single observation.

The following variables are provided to you:

* **id** : station identification code
* **date** : date in YYYY-MM-DD format (e.g. 2012-01-24 = January 24, 2012)
* **element** : indicator of element type
    * TMAX : Maximum temperature (tenths of degrees C)
    * TMIN : Minimum temperature (tenths of degrees C)
* **value** : data value for element (tenths of degrees C)

For this assignment, you must:

1. Read the documentation and familiarize yourself with the dataset, then write some python code which returns a line graph of the record high and record low temperatures by day of the year over the period 2005-2014. The area between the record high and record low temperatures for each day should be shaded.
2. Overlay a scatter of the 2015 data for any points (highs and lows) for which the ten year record (2005-2014) record high or record low was broken in 2015.
3. Watch out for leap days (i.e. February 29th), it is reasonable to remove these points from the dataset for the purpose of this visualization.
4. Make the visual nice! Leverage principles from the first module in this course when developing your solution. Consider issues such as legends, labels, and chart junk.


## Synopsis

I read the csv file called 'weather.csv,' removed the leap days, converted the named column 'Date' to a standard Date data type.

## Processing

You can also embed plots, for example:

```{r pressure, echo=FALSE}
#1. step one - set working directory
library(lubridate)
setwd("C:/Users/Elias/Desktop/weather/weather")

#2. step two - read the csv file

weather<-read.csv("../weather/weather.csv")

#3. changed the date format from factor to Date for the column Date
weather$Date<-ymd(weather$Date)

#4. get the year Date column
weather$'year'<-year(weather$Date)

#5. remove leap days
weather$'month'<-month(weather$Date)
#test
table(weather$month)
head(weather)
weather$'dayofyear'<-yday(weather$Date)
weather$'dayofmonth'<-day(weather$Date)
table(weather$day)
head(weather)

#expect 165002 rows found using nrow(rm_leap)

rm_leap<-weather[!(weather$dayofmonth==29 & weather$month==2),]
nrow(rm_leap)

#rm_leap not contain 29 for table(weather$day)
#5. create a dataframe where the year 2005 has been removed
df_2005to2014<-weather[weather$year!=2015,]



```


